---
title: "Classwork Activity"
author: "Johnathan Nguyen"
output: html_notebook
---


# Instructions (Step by Step)

## Step 1: Create fake data
```{r}
# Creating a small fake dataset
set.seed(2073) # allows for reproducibility 

students <- data.frame(
  Name = paste("Student", 1:20),
  StudyHours = round(runif(20, 1, 10), 1),
  Satisfaction = round(rnorm(20, mean = 7, sd = 1.5), 1),
  Major = sample(c("Data Science", "Business Analytics", "Math", "Computer Science"), 20, replace = TRUE)
)

head(students)
```


## Step 2: Drop a column

```{r}
# Remove the Name column
library(dplyr)
Students_Clean <- students %>% 
  select(-Name)

```


### Question:
Why might someone drop a column like name or ID from a dataset?
### Answer:
Because it is redundant to the list of numbers next to it


## Step 3: Visualize
```{r}
library(ggplot2)
```

```{r}
ggplot(Students_Clean, aes(x = Major, y = Satisfaction, fill = Major)) +
  geom_boxplot() +
  labs(
    title = "Student Satisfaction by Major",
    x = "Major",
    y = "Satisfaction (1–10)"
  ) +
  theme_minimal()
```


## Step 4: Explain: Write 2–3 sentences each

### Questions:

1. What pattern or difference do you see in the chart?
2. What might explain it?
3. Do you think this chart is accurate?
4. Why? Why not?

## Step 5: Questions on Git, GitHub and R Markdown

### Questions:

1. What does git add do?
2. What is the difference between git commit and git push?
3. Why is it useful to use GitHub for your code or data projects?
4. How could version control help when collaborating?
5. What is the difference between a code chunk and regular text in R Markdown?
6. How could R Markdown help you explain your analysis to someone else?

### Answers:
**Step 4:**  
1. Math students seem to have the most satisfaction while CS students have the lowest median.  The other two majors are between those two.  
2. This might be due to the workload and student expectations as some people might not have as much fun. An example is CS majors have a lot of coding classes most likely decreasing the satisfaction level.  
3. No  
4. Because even though it gives a general idea, the data set is only random. To make it more accurate you would need more observations that just 20.  

**Step 5:**  
1. Marks changes down in files to be included in the next commit
2. git commit saves changes to your local, while git push uploads those changes to something like GitHub
3. it makes it easy to store, save, and backup projects while tracking everything
4. It lets everyone work on the same project at the same time while not overwriting each others work and shows who did what
5. A code chunk is used to input code to show outputs like tables and graphs while a regular text you can use to explain the code
6. It helps show your analysis in one document while also allowing you to explain what you are doing for example you can have a code chunk and then explain what you are doing using regular text.